SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/ckdtree.tex
`cKDTree` -> \texttt{cKDTree}

The `cKDTree` module, which implements a space-partitioning data structure that
organizes points in $k$-dimensional space, was rewritten in C++ with templated classes. 
Support was added for periodic boundary conditions, which are often used 
in simulations of physical processes.

@@

In 2015 the cKDTree dual tree counting algorithm\cite{Moore2000ar}
was enhanced to support weights\cite{ckdtree-weights}, which are
essential in many scientific applications, e.g. computing correlation
functions of galaxies\cite{0004-637X-750-1-38}.

>>>>

The \texttt{cKDTree} module, which implements a space-partitioning data structure that
organizes points in $k$-dimensional space, was rewritten in C++ with templated classes. 
Support was added for periodic boundary conditions, which are often used 
in simulations of physical processes.

@@

In 2015 the \texttt{cKDTree} dual tree counting algorithm\cite{Moore2000ar}
was enhanced to support weights\cite{ckdtree-weights}, which are
essential in many scientific applications, e.g. computing correlation
functions of galaxies\cite{0004-637X-750-1-38}.
